---
title: "Airplane Safety"
author: "Shaik"
date: "2022-09-15"
output: word_document
---

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = TRUE)
```

# Description of the data

The airline safety data set contains data about the safety of different airlines from 1985 to 2014. The dataset is divided into two where the first 15 years (1985 - 1999) are placed in their own columns while the second 15 years (2000 - 2014) have separate columns. The data set contains 3 safety variables (number of incidents), number of fatal accidents and number of fatalities for each of the two time periods.In total, the dataset has 56 observations, each observation being a unique airline, and 8 variables.

```{r}
#read data using read.csv
airline_data <- read.csv(("https://raw.githubusercontent.com/fivethirtyeight/data/master/airline-safety/airline-safety.csv"))
#clean data (rename columns)
head(airline_data)

#Checking Structures
str(airline_data)


```

# Renaming Columns and Selecting variables

```{r}
#Loading dplyr package 
library(dplyr)

#Renaming Variables
airline_data <- airline_data %>%
  rename("incidents(1985-1999)"= "incidents_85_99",
         "fatal_accidents(1985-1999)" = "fatal_accidents_85_99",
         "fatalities(1985-1999)" = "fatalities_85_99",
         "incidents(2000-2014)" = "incidents_00_14",
         "fatal_accidents(2000-2014)" = "fatal_accidents_00_14",
         "fatalities(2000-2014)" = "fatalities_00_14")

#Variable Selection
Summary_data <- subset(airline_data, SELECT = -C(incidents(2000-2014), fatal_accidents(2000-2014),fatalities(2000-2014)))  
Summary_data


```

# Summary Statistics

```{r}
summary(Summary_data)
```
